---
title: 'Justinianic Plague Modelling: Time Course Figures'
author: "Lauren White"
date: "8/31/2019"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning = FALSE, cache=TRUE, tidy.opts=list(width.cutoff=80),tidy=TRUE)
```

## Load ODE functions and define initial conditions

* Load ODE functions from file `Plague_model_functions.R'
* Define initial conditions and expected values for each model
* Numerically integrate each ODE model or given set of parameters and initial conditions

```{r}
library(deSolve)
library(tidyr)
library(ggplot2)

source('~/JustinianPlague/Plague_model_functions.R')

time <- seq(0, 1000, by = 1) #how long to integrate over [time interval (days)]?

S_h0<-500000 #Intial condition- number of humans
N_r0<-S_h0 #Intial condition- number of rats

# Bubonic SIR: Flea/Rat/Human Model-----------------------------------

#Define initial conditions and parameter values
init <- c(S_r=N_r0-1, I_r=1, R_r=0, D_r=0, H=6, Fl=0, S_h = S_h0, I_h = 0, R_h=0, D_h=0) #population size, and how many individuals start in each susceptible, infected, or removed category for rats, fleas, and huamns
parameters <- c(beta_r = 1.248, alpha=3/N_r0, gamma_r = 1/5.15, g_r=0.06, r_f=0.0084, K_f=6, d_f=1/5, beta_h=0.19, gamma_h=1/10, g_h=0.34, b_h=1/(25*365), d_h=1/(25*365)) 

#Run ordinary differential equation solver
bubonicSIR_out <- as.data.frame(ode(y = init, times = time, func = bubonicSIR, parms = parameters))
bubonicSIR_out$time<-NULL

# Bubonic SEIR: Flea/Rat/Human Model----------------------------------

#Define initial conditions and parameter values
init <- c(S_r=N_r0-1, I_r=1, R_r=0, D_r=0, H=6, Fl=0, S_h = S_h0, E_h=0, I_h = 0, R_h=0, D_h=0)
parameters <- c(beta_r = 1.248, alpha=3/N_r0, gamma_r = 1/5.15, g_r=0.06, r_f=0.0084, K_f=6, d_f=1/5, beta_h=0.19, gamma_h=1/10, sigma_h= 1/4, g_h=0.34, b_h=1/(25*365), d_h=1/(25*365)) 

#Run ordinary differential equation solver
bubonicSEIR_out <- as.data.frame(ode(y = init, times = time, func = bubonicSEIR, parms = parameters))
bubonicSEIR_out$time<-NULL


# Bubonic SIR: Flea/Rat/Human Model with Rat Carrying Capacity & Resistance----------------------------------------------------------------

#Define initial conditions and parameter values
init <- c(S_r=N_r0-1, I_r=1, R_r=0, D_r=0, H=6, Fl=0, S_h = S_h0, I_h = 0, R_h=0, D_h=0)
parameters <- c(r_r=0.014, K_r=N_r0, p_r=0.65, d_r=0.00055, beta_r = 1.248, alpha=3/N_r0, gamma_r = 1/5.15, g_r=0.06, r_f=0.0084, K_f=6, d_f=1/5, beta_h=0.19, gamma_h=1/10, g_h=0.34, b_h=1/(25*365), d_h=1/(25*365)) 

#Run ordinary differential equation solver
bSIRrK_out <- as.data.frame(ode(y = init, times = time, func = bubonicSIRratK, parms = parameters))
bSIRrK_out$time<-NULL

# Bubonic SEIR: Flea/Rat/Human Model with Rat Carrying Capacity & Resistance----------------------------------------------------------------

#Define initial conditions and parameter values
init <- c(S_r=N_r0-1, I_r=1, R_r=0, D_r=0, H=6, Fl=0, S_h = S_h0, E_h=0, I_h = 0, R_h=0, D_h=0) #population size, and how many individuals start in each susceptible, infected, or removed category
parameters <- c(r_r=0.014, K_r=N_r0, p_r=0.65, d_r=0.00055, beta_r = 1.248, alpha=3/N_r0, gamma_r = 1/5.15, g_r=0.06, r_f=0.0084, K_f=6, d_f=1/5, beta_h=0.19, sigma_h= 1/4, gamma_h=1/10, g_h=0.34, b_h=1/(25*365), d_h=1/(25*365)) 

#Run ordinary differential equation solver
bSEIRrK_out <- as.data.frame(ode(y = init, times = time, func = bubonicSEIRratsK, parms = parameters))
bSEIRrK_out$time<-NULL

# Pneumonic plague SIR -------------------------------------------

#Define initial conditions and parameter values
init <- c(S_h = S_h0-1, I_h = 1, D_h=0) 
parameters <- c(beta_p = 0.08, gamma_p = 1/2.5, b_h=1/(25*365), d_h=1/(25*365)) 

#Run ordinary differential equation solver
pneumonic_out <- as.data.frame(ode(y = init, times = time, func = pneumonicSIR, parms = parameters))
pneumonic_out$time<-NULL

# Pneumonic Plague SEIR ------------------------------------------

#Define initial conditions and parameter values
init <- c(S_h = S_h0-1, E_h= 0, I_h = 1, D_h=0) 
parameters <- c(beta_p = 0.08, sigma_p= 1/4.3, gamma_p = 1/2.5, b_h=1/(25*365), d_h=1/(25*365)) 

#Run ordinary differential equation solver
pneumonicSEIR_out <- as.data.frame(ode(y = init, times = time, func = pneumonicSEIR, parms = parameters))
pneumonicSEIR_out$time<-NULL

# Bubonic/Pneumonic SEIR -----------------------------------------

#Define initial conditions and parameter values
init <- c(S_r=N_r0-1, I_r=1, R_r=0, D_r=0, H=6, Fl=0, S_h = S_h0, E_b=0, E_p=0, I_b = 0, I_p =0, R_h=0, D_h=0) 
parameters <- c(beta_r = 1.248, alpha=3/N_r0, gamma_r = 1/5.15, g_r=0.06, r_f=0.0084, K_f=6, d_f=1/5, beta_b=0.19, beta_p = 0.08, sigma_b= 1/4, sigma_p=1/4.3, gamma_b=1/10, gamma_p=1/2.5, p=0.10, g_h=0.34, b_h=1/(25*365), d_h=1/(25*365)) 

#Run ordinary differential equation solver
bp_out <- as.data.frame(ode(y = init, times = time, func = bubonic_pneumonicSEIR, parms = parameters))
bp_out$time<-NULL


#Maximum number of fatalities for each model

max(pneumonic_out$D_h)
max(pneumonicSEIR_out$D_h)
max(bubonicSIR_out$D_h)
max(bubonicSEIR_out$D_h)
max(bSIRrK_out$D_h)
max(bSEIRrK_out$D_h)
max(bp_out$D_h)

#Function to calculate how long outbreak has mortalities/day>100
calc_duration<-function(out){
 difference<-as.vector(NA)
  for(j in 2:length(out$D_h)){
    difference[j-1]<-out$D_h[j]-out$D_h[j-1]
  }
 # return(difference)
 return(c(length(which(difference>100)), length(which(difference>250)), max(difference)))
}

(pSIR_dur<-calc_duration(pneumonic_out))
(pSEIR_dur<-calc_duration(pneumonicSEIR_out))
(bSIR_dur<-calc_duration(bubonicSIR_out))
(bSEIR_dur<-calc_duration(bubonicSEIR_out))
(bSIRrK_dur<-calc_duration(bSIRrK_out))
(bSEIRrK_dur<-calc_duration(bSEIRrK_out)) 
(bp_dur<-calc_duration(bp_out))

```

## Figure 1

Plot comparing time courses of each of the hypothesized models using expected values.

```{r}
comp<- data.frame(time= time, pSIR=pneumonic_out$D_h, pSEIR=pneumonicSEIR_out$D_h, bSIR=bubonicSIR_out$D_h, bSEIR=bubonicSEIR_out$D_h, bSIRrK=bSIRrK_out$D_h, bSEIRrK=bSEIRrK_out$D_h, bpSEIR=bp_out$D_h)
write.csv(comp, "NumberDead2019_09_04.csv")

long_DF <- comp %>% gather(Model, NumberDead, c(pSIR, pSEIR, bSIR, bSEIR, bpSEIR, bSIRrK, bSEIRrK))

long_DF$Model <- as.character(long_DF$Model)
long_DF$Model <- factor(long_DF$Model, levels=c("pSIR", "pSEIR", "bSIR", "bSEIR", "bSIRrK", "bSEIRrK", "bpSEIR"))

tiff("Fig1.tiff", width=7, height=5, units="in", compression = "lzw", res=600)
g<-ggplot(long_DF, aes(time, NumberDead, col=Model)) + geom_line() +
  ylab("Number of Human Mortalities")+ xlab("Outbreak Duration (Days)")+
   scale_color_discrete(labels = c(pSIR="Pneumonic SIR", pSEIR="Pneumonic SEIR", bSIR="Bubonic SIR", bSEIR="Bubonic SEIR", bSIRrK="Bubonic SIR (Rat Dyn.)", bpSEIR="Bubonic & Pneumonic SEIR", bSEIRrK="Bubonic SEIR (Rat Dyn.)"))+
  theme_bw() + 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
g
dev.off()
g

```

## Repeat with different initial conditions


```{r}
S_h0<-500000 #Intial condition- number of humans
N_r0<-S_h0*0.5 #Intial condition- number of rats
```

```{r}
# Bubonic SIR: Flea/Rat/Human Model-----------------------------------

#Define initial conditions and parameter values
init <- c(S_r=N_r0-1, I_r=1, R_r=0, D_r=0, H=6, Fl=0, S_h = S_h0, I_h = 0, R_h=0, D_h=0) #population size, and how many individuals start in each susceptible, infected, or removed category for rats, fleas, and huamns
parameters <- c(beta_r = 1.248, alpha=3/N_r0, gamma_r = 1/5.15, g_r=0.06, r_f=0.0084, K_f=6, d_f=1/5, beta_h=0.19, gamma_h=1/10, g_h=0.34, b_h=1/(25*365), d_h=1/(25*365)) 

#Run ordinary differential equation solver
bubonicSIR_out <- as.data.frame(ode(y = init, times = time, func = bubonicSIR, parms = parameters))
bubonicSIR_out$time<-NULL

# Bubonic SEIR: Flea/Rat/Human Model----------------------------------

#Define initial conditions and parameter values
init <- c(S_r=N_r0-1, I_r=1, R_r=0, D_r=0, H=6, Fl=0, S_h = S_h0, E_h=0, I_h = 0, R_h=0, D_h=0)
parameters <- c(beta_r = 1.248, alpha=3/N_r0, gamma_r = 1/5.15, g_r=0.06, r_f=0.0084, K_f=6, d_f=1/5, beta_h=0.19, gamma_h=1/10, sigma_h= 1/4, g_h=0.34, b_h=1/(25*365), d_h=1/(25*365)) 

#Run ordinary differential equation solver
bubonicSEIR_out <- as.data.frame(ode(y = init, times = time, func = bubonicSEIR, parms = parameters))
bubonicSEIR_out$time<-NULL


# Bubonic SIR: Flea/Rat/Human Model with Rat Carrying Capacity & Resistance----------------------------------------------------------------

#Define initial conditions and parameter values
init <- c(S_r=N_r0-1, I_r=1, R_r=0, D_r=0, H=6, Fl=0, S_h = S_h0, I_h = 0, R_h=0, D_h=0)
parameters <- c(r_r=0.014, K_r=N_r0, p_r=0.65, d_r=0.00055, beta_r = 1.248, alpha=3/N_r0, gamma_r = 1/5.15, g_r=0.06, r_f=0.0084, K_f=6, d_f=1/5, beta_h=0.19, gamma_h=1/10, g_h=0.34, b_h=1/(25*365), d_h=1/(25*365)) 

#Run ordinary differential equation solver
bSIRrK_out <- as.data.frame(ode(y = init, times = time, func = bubonicSIRratK, parms = parameters))
bSIRrK_out$time<-NULL

# Bubonic SEIR: Flea/Rat/Human Model with Rat Carrying Capacity & Resistance----------------------------------------------------------------

#Define initial conditions and parameter values
init <- c(S_r=N_r0-1, I_r=1, R_r=0, D_r=0, H=6, Fl=0, S_h = S_h0, E_h=0, I_h = 0, R_h=0, D_h=0) #population size, and how many individuals start in each susceptible, infected, or removed category
parameters <- c(r_r=0.014, K_r=N_r0, p_r=0.65, d_r=0.00055, beta_r = 1.248, alpha=3/N_r0, gamma_r = 1/5.15, g_r=0.06, r_f=0.0084, K_f=6, d_f=1/5, beta_h=0.19, sigma_h= 1/4, gamma_h=1/10, g_h=0.34, b_h=1/(25*365), d_h=1/(25*365)) 

#Run ordinary differential equation solver
bSEIRrK_out <- as.data.frame(ode(y = init, times = time, func = bubonicSEIRratsK, parms = parameters))
bSEIRrK_out$time<-NULL

# Pneumonic plague SIR -------------------------------------------

#Define initial conditions and parameter values
init <- c(S_h = S_h0-1, I_h = 1, D_h=0) 
parameters <- c(beta_p = 0.08, gamma_p = 1/2.5, b_h=1/(25*365), d_h=1/(25*365)) 

#Run ordinary differential equation solver
pneumonic_out <- as.data.frame(ode(y = init, times = time, func = pneumonicSIR, parms = parameters))
pneumonic_out$time<-NULL

# Pneumonic Plague SEIR ------------------------------------------

#Define initial conditions and parameter values
init <- c(S_h = S_h0-1, E_h= 0, I_h = 1, D_h=0) 
parameters <- c(beta_p = 0.08, sigma_p= 1/4.3, gamma_p = 1/2.5, b_h=1/(25*365), d_h=1/(25*365)) 

#Run ordinary differential equation solver
pneumonicSEIR_out <- as.data.frame(ode(y = init, times = time, func = pneumonicSEIR, parms = parameters))
pneumonicSEIR_out$time<-NULL

# Bubonic/Pneumonic SEIR -----------------------------------------

#Define initial conditions and parameter values
init <- c(S_r=N_r0-1, I_r=1, R_r=0, D_r=0, H=6, Fl=0, S_h = S_h0, E_b=0, E_p=0, I_b = 0, I_p =0, R_h=0, D_h=0) 
parameters <- c(beta_r = 1.248, alpha=3/N_r0, gamma_r = 1/5.15, g_r=0.06, r_f=0.0084, K_f=6, d_f=1/5, beta_b=0.19, beta_p = 0.08, sigma_b= 1/4, sigma_p=1/4.3, gamma_b=1/10, gamma_p=1/2.5, p=0.10, g_h=0.34, b_h=1/(25*365), d_h=1/(25*365)) 

#Run ordinary differential equation solver
bp_out <- as.data.frame(ode(y = init, times = time, func = bubonic_pneumonicSEIR, parms = parameters))
bp_out$time<-NULL

#Maximum number of fatalities for each model

max(pneumonic_out$D_h)
max(pneumonicSEIR_out$D_h)
max(bubonicSIR_out$D_h)
max(bubonicSEIR_out$D_h)
max(bSIRrK_out$D_h)
max(bSEIRrK_out$D_h)
max(bp_out$D_h)

#Function to calculate how long outbreak has mortalities/day>100
calc_duration<-function(out){
 difference<-as.vector(NA)
  for(j in 2:length(out$D_h)){
    difference[j-1]<-out$D_h[j]-out$D_h[j-1]
  }
 # return(difference)
 return(c(length(which(difference>100)), length(which(difference>250)), max(difference)))
}

(pSIR_dur<-calc_duration(pneumonic_out))
(pSEIR_dur<-calc_duration(pneumonicSEIR_out))
(bSIR_dur<-calc_duration(bubonicSIR_out))
(bSEIR_dur<-calc_duration(bubonicSEIR_out))
(bSIRrK_dur<-calc_duration(bSIRrK_out))
(bSEIRrK_dur<-calc_duration(bSEIRrK_out)) 
(bp_dur<-calc_duration(bp_out))


```

## Figure S1

Plot comparing time courses of each of the hypothesized models using expected values.

```{r, echo=FALSE}
comp<- data.frame(time= time, pSIR=pneumonic_out$D_h, pSEIR=pneumonicSEIR_out$D_h, bSIR=bubonicSIR_out$D_h, bSEIR=bubonicSEIR_out$D_h, bSIRrK=bSIRrK_out$D_h, bSEIRrK=bSEIRrK_out$D_h, bpSEIR=bp_out$D_h)

long_DF <- comp %>% gather(Model, NumberDead, c(pSIR, pSEIR, bSIR, bSEIR, bpSEIR, bSIRrK, bSEIRrK))

tiff("FigS1.tiff", width=7, height=5, units="in", compression = "lzw", res=600)
S1<-ggplot(long_DF, aes(time, NumberDead, col=Model)) + geom_line() +
    xlab("Outbreak Duration (Days)") + ylab("Number Dead")+
  scale_color_discrete(labels = c(pSIR="Pneumonic SIR", pSEIR="Pneumonic SEIR", bSIR="Bubonic SIR", bSEIR="Bubonic SEIR", bSIRrK="Bubonic SIR (Rat Dyn.)", bpSEIR="Bubonic & Pneumonic SEIR", bSEIRrK="Bubonic SEIR (Rat Dyn.)"))+
  theme_bw() + 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
S1
dev.off()
S1
```


```{r}
S_h0<-500000 #Intial condition- number of humans
N_r0<-S_h0*2 #Intial condition- number of rats
```

```{r}
# Bubonic SIR: Flea/Rat/Human Model-----------------------------------

#Define initial conditions and parameter values
init <- c(S_r=N_r0-1, I_r=1, R_r=0, D_r=0, H=6, Fl=0, S_h = S_h0, I_h = 0, R_h=0, D_h=0) #population size, and how many individuals start in each susceptible, infected, or removed category for rats, fleas, and huamns
parameters <- c(beta_r = 1.248, alpha=3/N_r0, gamma_r = 1/5.15, g_r=0.06, r_f=0.0084, K_f=6, d_f=1/5, beta_h=0.19, gamma_h=1/10, g_h=0.34, b_h=1/(25*365), d_h=1/(25*365)) 

#Run ordinary differential equation solver
bubonicSIR_out <- as.data.frame(ode(y = init, times = time, func = bubonicSIR, parms = parameters))
bubonicSIR_out$time<-NULL

# Bubonic SEIR: Flea/Rat/Human Model----------------------------------

#Define initial conditions and parameter values
init <- c(S_r=N_r0-1, I_r=1, R_r=0, D_r=0, H=6, Fl=0, S_h = S_h0, E_h=0, I_h = 0, R_h=0, D_h=0)
parameters <- c(beta_r = 1.248, alpha=3/N_r0, gamma_r = 1/5.15, g_r=0.06, r_f=0.0084, K_f=6, d_f=1/5, beta_h=0.19, gamma_h=1/10, sigma_h= 1/4, g_h=0.34, b_h=1/(25*365), d_h=1/(25*365)) 

#Run ordinary differential equation solver
bubonicSEIR_out <- as.data.frame(ode(y = init, times = time, func = bubonicSEIR, parms = parameters))
bubonicSEIR_out$time<-NULL


# Bubonic SIR: Flea/Rat/Human Model with Rat Carrying Capacity & Resistance----------------------------------------------------------------

#Define initial conditions and parameter values
init <- c(S_r=N_r0-1, I_r=1, R_r=0, D_r=0, H=6, Fl=0, S_h = S_h0, I_h = 0, R_h=0, D_h=0)
parameters <- c(r_r=0.014, K_r=N_r0, p_r=0.65, d_r=0.00055, beta_r = 1.248, alpha=3/N_r0, gamma_r = 1/5.15, g_r=0.06, r_f=0.0084, K_f=6, d_f=1/5, beta_h=0.19, gamma_h=1/10, g_h=0.34, b_h=1/(25*365), d_h=1/(25*365)) 

#Run ordinary differential equation solver
bSIRrK_out <- as.data.frame(ode(y = init, times = time, func = bubonicSIRratK, parms = parameters))
bSIRrK_out$time<-NULL

# Bubonic SEIR: Flea/Rat/Human Model with Rat Carrying Capacity & Resistance----------------------------------------------------------------

#Define initial conditions and parameter values
init <- c(S_r=N_r0-1, I_r=1, R_r=0, D_r=0, H=6, Fl=0, S_h = S_h0, E_h=0, I_h = 0, R_h=0, D_h=0) #population size, and how many individuals start in each susceptible, infected, or removed category
parameters <- c(r_r=0.014, K_r=N_r0, p_r=0.65, d_r=0.00055, beta_r = 1.248, alpha=3/N_r0, gamma_r = 1/5.15, g_r=0.06, r_f=0.0084, K_f=6, d_f=1/5, beta_h=0.19, sigma_h= 1/4, gamma_h=1/10, g_h=0.34, b_h=1/(25*365), d_h=1/(25*365)) 

#Run ordinary differential equation solver
bSEIRrK_out <- as.data.frame(ode(y = init, times = time, func = bubonicSEIRratsK, parms = parameters))
bSEIRrK_out$time<-NULL

# Pneumonic plague SIR -------------------------------------------

#Define initial conditions and parameter values
init <- c(S_h = S_h0-1, I_h = 1, D_h=0) 
parameters <- c(beta_p = 0.08, gamma_p = 1/2.5, b_h=1/(25*365), d_h=1/(25*365)) 

#Run ordinary differential equation solver
pneumonic_out <- as.data.frame(ode(y = init, times = time, func = pneumonicSIR, parms = parameters))
pneumonic_out$time<-NULL

# Pneumonic Plague SEIR ------------------------------------------

#Define initial conditions and parameter values
init <- c(S_h = S_h0-1, E_h= 0, I_h = 1, D_h=0) 
parameters <- c(beta_p = 0.08, sigma_p= 1/4.3, gamma_p = 1/2.5, b_h=1/(25*365), d_h=1/(25*365)) 

#Run ordinary differential equation solver
pneumonicSEIR_out <- as.data.frame(ode(y = init, times = time, func = pneumonicSEIR, parms = parameters))
pneumonicSEIR_out$time<-NULL

# Bubonic/Pneumonic SEIR -----------------------------------------

#Define initial conditions and parameter values
init <- c(S_r=N_r0-1, I_r=1, R_r=0, D_r=0, H=6, Fl=0, S_h = S_h0, E_b=0, E_p=0, I_b = 0, I_p =0, R_h=0, D_h=0) 
parameters <- c(beta_r = 1.248, alpha=3/N_r0, gamma_r = 1/5.15, g_r=0.06, r_f=0.0084, K_f=6, d_f=1/5, beta_b=0.19, beta_p = 0.08, sigma_b= 1/4, sigma_p=1/4.3, gamma_b=1/10, gamma_p=1/2.5, p=0.10, g_h=0.34, b_h=1/(25*365), d_h=1/(25*365)) 

#Run ordinary differential equation solver
bp_out <- as.data.frame(ode(y = init, times = time, func = bubonic_pneumonicSEIR, parms = parameters))
bp_out$time<-NULL

#Maximum number of fatalities for each model

max(pneumonic_out$D_h)
max(pneumonicSEIR_out$D_h)
max(bubonicSIR_out$D_h)
max(bubonicSEIR_out$D_h)
max(bSIRrK_out$D_h)
max(bSEIRrK_out$D_h)
max(bp_out$D_h)

#Function to calculate how long outbreak has mortalities/day>100
calc_duration<-function(out){
 difference<-as.vector(NA)
  for(j in 2:length(out$D_h)){
    difference[j-1]<-out$D_h[j]-out$D_h[j-1]
  }
 # return(difference)
 return(c(length(which(difference>100)), length(which(difference>250)), max(difference)))
}

(pSIR_dur<-calc_duration(pneumonic_out))
(pSEIR_dur<-calc_duration(pneumonicSEIR_out))
(bSIR_dur<-calc_duration(bubonicSIR_out))
(bSEIR_dur<-calc_duration(bubonicSEIR_out))
(bSIRrK_dur<-calc_duration(bSIRrK_out))
(bSEIRrK_dur<-calc_duration(bSEIRrK_out)) 
(bp_dur<-calc_duration(bp_out))


```

### Figure S2

Plot comparing time courses of each of the hypothesized models using expected values.

```{r}
comp<- data.frame(time= time, pSIR=pneumonic_out$D_h, pSEIR=pneumonicSEIR_out$D_h, bSIR=bubonicSIR_out$D_h, bSEIR=bubonicSEIR_out$D_h, bSIRrK=bSIRrK_out$D_h, bSEIRrK=bSEIRrK_out$D_h, bpSEIR=bp_out$D_h)

long_DF <- comp %>% gather(Model, NumberDead, c(pSIR, pSEIR, bSIR, bSEIR, bpSEIR, bSIRrK, bSEIRrK))

tiff("FigS2.tiff", width=7, height=5, units="in", compression = "lzw", res=600)
S2<-ggplot(long_DF, aes(time, NumberDead, col=Model)) + geom_line() +
  xlab("Outbreak Duration (Days)") + ylab("Number Dead")+
  scale_color_discrete(labels = c(pSIR="Pneumonic SIR", pSEIR="Pneumonic SEIR", bSIR="Bubonic SIR", bSEIR="Bubonic SEIR", bSIRrK="Bubonic SIR (Rat Dyn.)", bpSEIR="Bubonic & Pneumonic SEIR", bSEIRrK="Bubonic SEIR (Rat Dyn.)"))+
  theme_bw() + 
  theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
S2
dev.off()
S2
```

